---
title: "Accessing the Discourse API from R"
---

```{r}
library(tidyverse)
source('discourse.R')
```

## Overview

This is a basic R client for the bits of the Discourse API we need to use at Plymouth.
It mostly focusses on group membership right now.

It should probably become a package at some point...


## Make a connection object

This mostly just encapsulates connection strings for making http requests:


```{r}
dc <- discourseconnection("https://discourse.psy.plymouth.ac.uk/",
                          rstudioapi::askForPassword(prompt = "Enter your API Key Here:"),
                          "system")

print(dc$connection)
```
But it also stores some info about the instance:

```{r}
names(dc)
```

For example groups:

```{r}
dc$groups
```



## List groups and group members

```{r}
groups(dc)$name
```


```{r}
agroup <- groups(dc)$name %>% first(1)
group_members(dc, group_id=agroup)
```


## Amend groups

```{r}
add_group_members(dc, "test", usernames="bjw22")
group_members(dc, group_id='test') %>% filter(username=="bjw22")
```

```{r}
remove_group_members(dc, "test", usernames="bjw22")
group_members(dc, group_id='test') %>% filter(username=="bjw22") 
```



# Todo

- Upload avatars for students: https://docs.discourse.org/#tag/Uploads
- Activity stats for non-engagers












